### 2020-06-10 writeup/proof_examples.tex
supp wip

\subsection{Missing Proofs of Section \ref{sec_similarity}}\label{app_proof_31}

@@

\subsection{Missing Proofs of Section \ref{sec_data_size}} \label{app_proof_32}
We first prove Proposition \ref{prop_data_size}, which describes the effect of source/task data ratio on the information transfer.

@@

\subsection{Missing Proofs of Section \ref{sec_covshift}}\label{app_proof_33}

>>>>

\subsection{Missing Proofs for Task Similarity}\label{app_proof_31}

@@

\subsection{Missing Proofs for Sample Size} \label{app_proof_32}
We first prove Proposition \ref{prop_data_size}, which describes the effect of source/task data ratio on the information transfer.

@@

\subsection{Missing Proofs for Covariate Shift}\label{app_proof_33}
